---
title: "Visualize Data"
author: "Rachel Ramos"
format: gfm
---


```{r}
#| label: setup
#| include: false
library(tidyverse)
```



## Your Turn 0

Add a setup chunk that loads the tidyverse packages.


```{r}
#| label: print out data
head(mpg)
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
#| label: mpg_map_scatter
ggplot(mpg) + #can add just the data set.. initializing plot with ggplot.. plus always at the end 
  geom_point(aes(x=displ, y = hwy)) #mapping aesthetics then labels x and y axis.. adding layers
```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
#| label: Boxplot
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.

```{r}
#| label: histogram 
ggplot(data=mpg) + 
  geom_histogram(mapping=aes(x=hwy))
```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.

```{r}
#| label: histogram binwidth mod
ggplot(data=mpg) + 
  geom_histogram(mapping=aes(x=hwy) , binwidth = 2)
```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
#| label: Scatterplot for mileage
ggplot(data=mpg) + 
  geom_point(mapping=aes(x=displ,
                         y=hwy,
                         color=class))+
  labs( x="Engine Size Displacemnet",
        y= " Highway Mileage",
        color= "Class of Vehicle",
        title= "The Bigger the Engine the Less Mileage We Get on the Highway")+ 
  theme_light()
                         #shape=class
                         #alpha=class
                         #size = class
               
```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
#| label: Mulitple plots
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl) #creates colomns(4), 1 row
q + facet_grid(drv ~ .) #creates rows (4), 1 col
q + facet_grid(drv ~ cyl) #creates rows and columns 4&4
q + facet_wrap(~ class) #creates rows and columns for each class
```


## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}

ggplot(data=mpg) + 
  geom_bar(mapping = aes(x=class, fill= class)) + guides(fill= "none") + 
  labs(x=" Class of Vehicle",
       y= "Nuber of Vehicles in Sample")

     

#ggplot(data=mpg) + 
 # geom_bar(mapping = aes(x=class, fill= class)) + guides(fill= "none") + 
 # labs(x=" Class of Vehicle",
       #y= "Nuber of Vehicles in Sample",
      # theme_bw()
```


```{r}

ggplot(data=mpg) + 
  geom_bar(mapping = aes(x=class, fill= drv), 
           position=position_dodge())+ 
  labs(x=" Class of Vehicle",
       y= "Nuber of Vehicles in Sample",
       fill= "Type of drive" )

```

## Quiz

What will this code do?

```{r}
#| label: Combined scatter
ggplot( mpg, aes( x=displ, y=hwy))+ 
  geom_point(aes(color=class))+
  geom_smooth(color="black",
              se=FALSE,
              method="lm")+
  scale_color_viridis_d()

  ggsave("my-plot.jpg", width =6, height=4)
  #code will add new layers
```


***

# Take aways

You can use this code template to make thousands of graphs with **ggplot2**.

```{r eval = FALSE}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```